Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-04-30 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
added additional comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@

If our algorithm does not find a feasible solution among the item of equipment that were provided to our synthesis algorithm, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution. It indicates that was not possible to combine the itens of each equipment and create a feasible solution. The main challenge for the verification part is to find a feasible solution (technically speaking, regarding the constraints and user requirements), which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our synthesis algorithm. \textcolor{red}{An unfeasible solution happens due to the incomplete list of equipment?}

>>>>

\textcolor{red}{Could you please adapt this text to our context?}

@@

If our algorithm does not find a feasible solution among the item of equipment that were provided to our synthesis algorithm, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution. It indicates that was not possible to combine the itens of each equipment and create a feasible solution. The main challenge for the verification part is to find a feasible solution (technically speaking, regarding the constraints and user requirements), which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our synthesis algorithm. \textcolor{red}{An unfeasible solution happens due to the incomplete list of equipment?} \textcolor{red}{Could we synthesize the equipment that we need to meet the user requirements?}
